Covariates analysis of MSBB RNASeq data of region BM 36 (realigned from source FASTQ with STAR-HTSeq)

### 2016-09-12 code/Rmd/MSSM_BM_36_RNASeq_Realigned_StarHTSeq.Rmd
Added markdown to process Star Htseq aligned BM 36

---
title: "Covariates analysis of MSBB RNASeq data of region BM 44 (realigned from source FASTQ with STAR-HTSeq)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(synapseClient)
library(knitr)
library(githubr)

@@

knit2synapse::knitToFolderEntity(file = "./MSSM_BM_44_RNASeq_Realigned_StarHTSeq.Rmd",
                                 parentId ="syn5570248",
                                 entityName = 'MSBB BM 44 RNASeq RealignedFromSource StarHTSeq')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
# Synapse parameters
parentId = 'syn5570248';
activityName = 'Covariate analysis';
activityDescription = 'Covariate analysis of MSBB BM 44 RNASeq samples';

thisFileName <- 'MSSM_BM_44_RNASeq_Realigned_StarHTSeq.Rmd'

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
Data were obtained from AMP-AD portal of MSSM, and following brain regions were analysed for differential expression between case and control:
  | Region | Name                        | 
  | :----- | --------------------------- | 
  | BM_44  | inferior frontal Gyrus (IFG)|

* BM 44: pars opercularis (of the inferior frontal gyrus), and it refers to a subdivision of the frontal region of cerebral cortex.

Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
# Download expression data
COUNT_ID <- 'syn7221166'
ALL_USED_IDs <- COUNT_ID
COUNT <- read.table(synGet(COUNT_ID)@filePath, quote = '', header = T, sep = '\t')

@@

METADATA = left_join(METADATA_TECHNICAL %>%
                       dplyr::mutate(ID = gsub('hB_RNA_','',NewBarcode),
                                     ID = as.numeric(ID)),
                     METADATA_CLINICAL %>%
                       dplyr::select(BB, BM.44.Barcode, PMI, RACE, 
                                     AOD, CDR, SEX, NP.1, PlaqueMean, bbscore) %>%
                       dplyr::rename(BM_44 = BM.44.Barcode) %>%
                       tidyr::gather(BrainRegion, ID, -BB, -PMI, -RACE, 
                                     -AOD, -CDR, -SEX, -NP.1, -PlaqueMean, -bbscore) %>%
                       filter(!is.na(ID)) %>%
                       dplyr::mutate(ID = as.numeric(ID))) %>%
  inner_join(SampleID) %>%
  filter(!is.na(SampleID)) %>%
  unique
rownames(METADATA) = METADATA$SampleID

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=factor(Batch), shape=as.factor(CDR), size=as.numeric(PMI)))
p <- p + theme_bw() + theme(legend.position="top") + scale_shape_manual(values = 1:7)
# p <- p + geom_text(aes(label= ID), size=4, hjust=0)
p

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "MSBB BM 44 RNASeq  RealignedFromSource StarHTSeq", parentId = parentId)
CODE <- synStore(CODE)

>>>>

---
title: "Covariates analysis of MSBB RNASeq data of region BM 36 (realigned from source FASTQ with STAR-HTSeq)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(synapseClient)
library(knitr)
library(githubr)

@@

knit2synapse::knitToFolderEntity(file = "./MSSM_BM_36_RNASeq_Realigned_StarHTSeq.Rmd",
                                 parentId ="syn5570248",
                                 entityName = 'MSBB BM 36 RNASeq RealignedFromSource StarHTSeq')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
# Synapse parameters
parentId = 'syn5570248';
activityName = 'Covariate analysis';
activityDescription = 'Covariate analysis of MSBB BM 36 RNASeq samples';

thisFileName <- 'MSSM_BM_36_RNASeq_Realigned_StarHTSeq.Rmd'

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```

Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
# Download expression data
COUNT_ID <- 'syn7224673'
ALL_USED_IDs <- COUNT_ID
COUNT <- read.table(synGet(COUNT_ID)@filePath, quote = '', header = T, sep = '\t')

@@

METADATA = left_join(METADATA_TECHNICAL %>%
                       dplyr::mutate(ID = gsub('hB_RNA_','',NewBarcode),
                                     ID = as.numeric(ID)),
                     METADATA_CLINICAL %>%
                       dplyr::select(BB, BM36.Fnl, PMI, RACE, 
                                     AOD, CDR, SEX, NP.1, PlaqueMean, bbscore) %>%
                       dplyr::rename(BM_36 =  BM36.Fnl) %>%
                       tidyr::gather(BrainRegion, ID, -BB, -PMI, -RACE, 
                                     -AOD, -CDR, -SEX, -NP.1, -PlaqueMean, -bbscore) %>%
                       filter(!is.na(ID)) %>%
                       dplyr::mutate(ID = as.numeric(ID))) %>%
  inner_join(SampleID) %>%
  filter(!is.na(SampleID)) %>%
  filter(!(ID %in% c(335:341, 10567, 10622, 10577))) %>%
  unique
rownames(METADATA) = METADATA$SampleID

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=factor(Batch), shape=as.factor(CDR), size=as.numeric(PMI)))
p <- p + theme_bw() + theme(legend.position="top") + scale_shape_manual(values = 1:7)
p <- p + geom_text(aes(label= ID), size=4, hjust=1)
p

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "MSBB BM 36 RNASeq  RealignedFromSource StarHTSeq", parentId = parentId)
CODE <- synStore(CODE)
